Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-04-13 scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex

\author{%
Nick Hawes \\ Intelligent Robotics Lab \\ University of Birmingham, UK \\ n.a.hawes@cs.bham.ac.uk 
\And % 
Matthew Klenk \\ Palo Alto Research Center \\  Palo Alto, CA \\ matthew.klenk@parc.com 
\And % 
Kate Lockwood \\ ITCD Department \\ California State University - Monterey Bay \\ klockwood@csumb.edu  
\AND % 
Graham S. Horn \\ Intelligent Robotics Lab \\ University of Birmingham, UK \\ gsh148@cs.bham.ac.uk 
\And % 
John Kelleher \\ Applied Intelligence Research Centre \\ Dublin Institute of Technology \\ john.d.kelleher@dit.ie}

@@

% The authors would like to thank Jeffery Usher for providing the code to compute Voronoi diagrams, Scott Friedman for assistance on probablistic SME, and Danny Bobrow comments on an earlier draft of this paper.

The research leading to these results has received funding from the European Community's Seventh Framework Programme [FP7/2007-2013] under grant agreement No. 215181, CogX.

>>>>

\author{%
Nick Hawes \\ Intelligent Robotics Lab \\ University of Birmingham, UK \\ n.a.hawes@cs.bham.ac.uk 
\And % 
Matthew Klenk \\ Palo Alto Research Center \\  Palo Alto, CA \\ matthew.klenk@parc.com 
\And % 
Kate Lockwood \\ ITCD Department \\ California State University - Monterey Bay \\ klockwood@csumb.edu  
\AND % 
Graham S. Horn \\ Intelligent Robotics Lab \\ University of Birmingham, UK \\ gsh148@cs.bham.ac.uk 
\And % 
John D. Kelleher \\ Applied Intelligence Research Centre \\ Dublin Institute of Technology \\ john.d.kelleher@dit.ie}

@@

The research leading to these results has received funding from the European Community's Seventh Framework Programme [FP7/2007-2013] under grant agreement No. 215181, CogX. The authors would like to thank Jeffery Usher for providing the code to compute voronoi diagrams, Scott Friedman for assistance on probabilistic SME, and Danny Bobrow comments on an earlier draft of this paper.
